\section{Interconnection Measurement Project: Data}\label{sec:data}

In this section, we discuss the availability of various datasets. We
discuss both what we CITP receives, as well as what data we make
publicly available. We can only publicly release aggregated data that
does not reveal individual ISP information, due to the need to protect
proprietary information, such as network architecture and business
relationships.



\if 0
\subsection{Private Data}

Information about utilization at individual interconnection points is
not available in the publicly available data, making it difficult to
assess whether or not a particular interconnection point is
congested. Each ISP collects and makes private the individual traffic
flow statistics for individual flows, yet much of this data is not made
public, due to various contractual and business relationships. The
private datasets contain the following information which is either
directly or indirectly evident from traffic statistics: 
\begin{itemize}
\item	{\em Directional traffic volume ratios.} As part of contractual
  arrangements, ISP typically maintain contingencies about the ratio of
  traffic that flows in each direction across an interconnect. These
  ratios form an important cornerstone in many proprietary contractual
  relationships. 
\item {\em Traffic volume mixes by application type.} For competitive
  reasons, ISPs may wish to keep private specific information about the
  volumes of traffic for individual applications or to specific
  destinations.Traffic volumes to specific destinations may be
  particularly sensitive, as these volumes reveal the relationships that
  an ISP’s customers may have with other Internet destinations.
\end{itemize}

The aggregation of the public data reflects the need to keep this type
of information about contracts private. 
\fi
